# Checking the hypothesis that the callback is made when the item is set up.

```{r include=FALSE}
require(WriteScoreR)
newScorerSet("banner-ignore")
```


### Free Text
`r I(textItem(rows=1,totalPts=1))`
`r I(textItem(rows=1,totalPts=2))`
`r I(textItem(rows=1,totalPts=3))`
`r I(textItem(rows=1,totalPts=4))`
`r I(textItem(rows=1,totalPts=5))`
`r I(textItem(rows=1,totalPts=6))`
`r I(textItem(rows=1,totalPts=7))`
`r I(textItem(rows=1,totalPts=8))`
`r I(textItem(rows=1,totalPts=9))`
`r I(textItem(rows=1,totalPts=10))`


### Select from a set

`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`     
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`    
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`     
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`    
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   
`r I(selectNumber(choices=c(3,9),correct=3,totalPts=2))`   

### Multiple Choice

```{r include=FALSE}
f = newMC(totalPts=1)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=2)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=3)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=4)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=5)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=6)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=7)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=8)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=9)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

```{r include=FALSE}
f = newMC(totalPts=10)
```

- `r I(f(FALSE))` The value of $a x^2 + b x - c$ for all $a$, $b$, and $c$
- `r I(f(TRUE))`  $e^{i\pi}$
- `r I(f(FALSE))` $\ln(0)$
- `r I(f(FALSE))` There's no such thing as a negative number, just a negative attitude. 

```{r results="hide"} 
I(f(finish=TRUE))
```

