Testing the WriteScoreR Package for Rmd files
========================================================

### Danny Kaplan
### May 21, 2013

This problem tests the `WriteScoreR` package.

First, you must load the package:
```{r message=FALSE,warning=FALSE}
require(WriteScoreR)
```
Generally you will want to do this with an `include=FALSE` directive.

Next, give a unique ID to the set of items.
```{r}
newScorerSet("test1-v0.1")
```

Put any answers in an "aside" HTML FLAG
<aside>This will only be shown when the answers are on.</aside> But this will be shown all the time.
<aside>Here's another aside.</aside>

Now you can ask your questions:

### A Multiple Choice




When in the course of human events ...
```{r}
f = newMC(pts=5) # Ordinarily, make this silent
```
`r I(f(FALSE))` "you decide to bail."
`r I(f(TRUE))` "it becomes necessary ..."
`r I(f(FALSE))` "you've got to do what you've got to do ..." 
`r I(f(finish=TRUE))`

Which of these in in Europe?

`r f = newMC(pts=5,markers=c("First","Second","Third","Fourth")) # Ordinarily, make this silent`

- `r I(f(TRUE))` Albania
- `r I(f(FALSE))` Brazil
- `r I(f(FALSE))` China 
`r I(f(finish=TRUE))`

#### And another

What's the answer? `r f = newMC(pts=5)` 

`r I(f(TRUE))` Chatty, but not as long as writing something like $x^2 \sqrt{x}$

`r I(f(FALSE))` Short and to the point, but with a `variable`

`r I(f(FALSE))` Long and repetetive, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, over and over, 

`r I(f(finish=TRUE))`


What's your opinion? `r I(textItem(name="try text",rows=1))`

Do you care to revise that? `r I(textItem(name="revise text"))`

You may find it easier to define the items in one place and use them in another:
```{r}
spainrain = choiceItem(Algeria=list(pts=0,hint="Wrong continent"),
                       Spain=list(pts=2,reward="My Fair Lady!"))
hurricanes= choiceItem(often=list(pts=0),usually="no","hardly ever"="yes")
```

* The rain in BLANK falls mainly on the plain. `r I(spainrain)`
* In Hartford, Hereford and Hampshire, hurricanes BLANK happen: `r I(hurricanes)`
