Example ScoreR Markup
=========================

### Boilerplate at the top

Usually, this would be hidden with a knitr `include=FALSE` directive:
```{r}
require("ScoreR")
startProblem("example-1-2013/07/30")
```

### Multiple Choice

What day is bad news for Caesar?  
```{r}
Q <- newMC(name="example", totalPts=4)
```

`r I(Q(FALSE))` The Fourth of July  
`r I(Q(TRUE))` The Ides of March  
`r I(Q(credit=.5))` The days around the Ides of March  
`r I(Q(finish=TRUE))`

Note: In markdown, putting two or more empty spaces at the end of a line causes a line break.  That's what was used to separate the items here.  The item selectors themselves are being generated with knitr code like `I(Q(FALSE))`
    
What day is associated with independence?  
```{r}
Q <- newMC(name="anotherexample", totalPts=4)
```

`r I(Q(TRUE))` The Fourth of July  
`r I(Q(FALSE))` The Ides of March  
`r I(Q(finish=TRUE))`


### Text Entry

Free text entry:

`r I(textItem(name="first",totalPts=3))`

### Select from a Set

Which one of these things swims? `r I(selectSet(name="swim",totalPts=5,Fish=TRUE,Dog=TRUE,Tree=FALSE,Chair=FALSE))`


### Numerical Entry

Not yet implemented ...
`r I(numberItem(ans=pi))`


### Finish up at the end of the problem

This also will usually be hidden, with a knitr `include=FALSE` directive

```{r results="asis"}
I(endProblem())
```